The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-13 analysis/paper/paper.qmd

### Tokenisation
Word-level tokenisation was applied with the `unnest_tokens()` function of the 
`tidytext` package. This was preferred over other tokenisers as it produced 
results that work seamlessly with other `tidyverse` tools.

### Stop words
- Three types of stop words: global, subject-specific and document stop words.
- Global stop words:
  - All theses were written in English, so for common English stop words the "snowball" lexicon was used
  - Optionally, try creating a custom stop word list on the entire corpus, by removing high-frequency words, starting with 20 words and increasing by 10 until reaching words that are not appropriate as stop words
- Subject-specific stop words:
  - Manually constructed list, needs domain knowledge
  - Words that are commonly used to structure a theses, such as "preface", "contents", and "introduction", were added as custom stop words
- Document stop words:
  - Stop words from titles and author names should only be removed from corresponding theses

>>>>

### Tokenisation

Word-level tokenisation was applied with the `unnest_tokens()` function of the `tidytext` package. This was preferred over other tokenisers as it produced results that work seamlessly with other `tidyverse` tools.

### Stop words

-   Three types of stop words: global, subject-specific and document stop words.
-   Global stop words:
    -   All theses were written in English, so for common English stop words the "snowball" lexicon was used
    -   Optionally, try creating a custom stop word list on the entire corpus, by removing high-frequency words, starting with 20 words and increasing by 10 until reaching words that are not appropriate as stop words
-   Subject-specific stop words:
    -   Manually constructed list, needs domain knowledge
    -   Words that are commonly used to structure a theses, such as "preface", "contents", and "introduction", were added as custom stop words
-   Document stop words:
    -   Stop words from titles and author names should only be removed from corresponding theses
